---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 8pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\par\centering{\Large{\textbf{Darwin Del Castillo, MD MPH}}}
\vspace{-5pt}
```{r address, include = FALSE, echo = FALSE, eval=FALSE}
\par\centering{\textit{Address:} 4545 8th Ave NE, Seattle, WA 98105}
\vspace{-5pt}
```
\par\centering{\textit{Mobile:} +1 (206) 605 5077}
\vspace{-5pt}
\par\centering{\textit{Email:} ddelcastillo.f@gmail.com}
\vspace{-5pt}
\par\centering{\href{https://www.linkedin.com/in/darwin-del-castillo-md/}{LinkedIn} | \href{https://github.com/ddelcastillof}{Github}}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\vspace{-10pt}

```{r brief bio, eval = FALSE, include = FALSE, echo = FALSE}
\section{\underline{Summary}}
\justifying{Medical doctor and global health scientist with extensive experience bridging the gap between epidemiological methods and healthcare data science. I am committed to transforming early-life health outcomes through innovative research and data-driven solutions. I have collaborated with a diversity of global health institutions and managing research teams that translates data findings into actionable public health information.}
```
\section{\underline{Education}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master in Public Health (MPH)} & \textbf{Sep 2023 – May 2025} \\
\textbf{University of Washington, Seattle - USA} & \\
\textit{Thesis: }“Cost-effectiveness analysis of a household salt substitute intervention on reducing community-wide blood pressure in Northern Peru” & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textbf{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\textit{Thesis: }“Childhood Obesity and Its Effect on Academic Achievement: An Analysis of the Young Lives Study between 2009 and 2016” &\\

\end{longtable}
\section{\underline{Professional Experience}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 - Current} \\
\multicolumn{2}{p{18cm}}{\textbf{Clinical Informatics Team, Institute for Health Metrics and Evaluation}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Pooling epidemiological data of lower respiratory tract infections due to human metapneumovirus from 2010 to 2023 using the package meta in R and Python functions.
\item Estimated population-attributable fractions and standardized mortality ratios for socially excluded groups in high-income countries using R.
\item Analyzed data from public sources using Markov Chain Monte Carlo algorithms to estimate the overlap proportion between socially excluded groups in high-income countries using R.
\end{itemize}
} \\

\textbf{Graduate Research Assistant} & \textbf{Jun 2024 - Mar 2025} \\
\multicolumn{2}{p{18cm}}{\textbf{Department of Global Health}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Conducted a scoping review protocol and performing evidence synthesis for mapping potential indicators for implementing mental health policy in data-limited settings.
\item Designed of a mixed-method study protocol to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting.
\item Crafted communication strategies with stakeholders to inform results from the mixed-methods study.
\end{itemize}
} \\

\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 - Mar 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Population Research Center, Department of Health Systems and Population Health}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Carried out on-phone interviews for the ReOpening Schools Safely and Educating Youth Study post-survey assessments.
\item Facilitated the submission of materials in Spanish to the IRB for Alzheimer’s Disease Research Center (ADRC).
\item Conducted preliminary analyses for the Outreach, Engagement, and Recruitment module of the ADRC Clinical Core Study project.
\end{itemize}
} \\

\textbf{Research Consultant} & \textbf{Jan 2023 - Jan 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Technology Assessment Direction, Health Technology Assessment and Research Institute}} \\
\multicolumn{2}{p{18cm}}{\textbf{Social Security Health System, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Elaborated policy documents of new pharmaceutical products for Peru’s social health insurance using a mixture of real-world evidence and economic data.
\item Conducted systematic reviews of anti-cancerous and immunosuppressant drugs regarding efficacy and economic impact.
\item Evaluated the budget impact of introducing new pharmacological products in Peruvian social health insurance.
\end{itemize}
} \\

\textbf{Clinical Sub-investigator} & \textbf{Mar 2022 - Mar 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{Via Libre Association}} \\
\multicolumn{2}{p{18cm}}{\textbf{Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Recruited patients identified as queer for clinical studies in STI and HIV prevention and treatment.
\item Performed clinical procedures and activities associated with the normal operation of clinical trials funded by NIH and pharmaceutical companies.
\item Participated and organized activities for community outreach and participant retention crafted for the queer community.
\end{itemize}
} \\

\newpage

\textbf{Research Assistant} & \textbf{Mar 2019 - Aug 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{CRONICAS Center of Excellence in Chronic Diseases}} \\
\multicolumn{2}{p{18cm}}{\textbf{Universidad Peruana Cayetano Heredia, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Coordinated focus groups and on-field work across four Peruvian regions to co-design an intervention for patients with cognitive impairment and their caregivers.
\item Contributed to research grant proposals in hypertension, diabetes, cancer, and multimorbidity projects by conducting systematic reviews and preliminary data analysis.
\item Co-authored scientific manuscripts in the topics mentioned above which included longitudinal data analyses, meta-analyses, and unsupervised machine learning methods using Stata and R.
\end{itemize}
} \\

\end{longtable}

\section{\underline{Additional Education}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

```{r teaching, eval = FALSE, include = FALSE, echo = FALSE}
\section{\underline{Teaching Experience}}
\subsection{Courses taught at the college level}
\subsubsection{Courses taught at Universidad Nacional Mayor de San Marcos}

df <- get_cv_sheet('classes') |> filter(univ == "UNMSM") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type,
      semester = ifelse(semester == 'Aut20', 'Aut20', semester)
    ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center")

\subsubsection{Courses taught at University of Washington}

df <- get_cv_sheet('classes') |> filter(univ == "UW") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type, 
      semester = ifelse(semester == 'Spr24', 'Spr24', semester)
      ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center")

\subsection{Other teaching experience}
teaching <- get_cv_sheet('teaching') |>
  arrange(desc(date)) |> 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    url = ifelse(is.na(url), NA, markdown_url(url)),
    date = ifelse(is.na(url), date, paste0(date, '. ', url)), 
    citation = paste(title, host, location, date, sep = '. ')
  )

\subsubsection{Seminars}

#| results: asis
make_ordered_list_filtered(teaching, "seminar")

\section{\underline{Advising}}
```

\section{\underline{Skills}}

\begin{justify}
\textbf{Computer and programming skills:} 
\begin{itemize}
\item \textbf{Programming languages:} R, Python, bash
\item \textbf{Statistical software:} Stata, SPSS, SAS, G*Power
\item \textbf{Data visualization and reporting:} Shiny, ArcGIS, \LaTeX, Markdown,
\item \textbf{Data management and wrangling:} SQL, REDCap
\item \textbf{Project management:} Jira, Asana, Trello
\item \textbf{Development tools:} Git, GitHub, Docker, VSCode, Confluence, Bitbucket 
\item \textbf{Computing environments:} Linux/Unix, Windows, ssh
\end{itemize}

\textbf{Languages:} 
\begin{longtable}{>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}}
English: Fluent & Spanish: Native & Portuguese: Working proficiency
\end{longtable}
\end{justify}

\section{\underline{Publications}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0(journal_abbv)),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r printing references in pandoc format}
#| results: asis
make_ordered_list_filtered(pubs, "peer_reviewed")
```

\section{\underline{Leadership and Service}}
\subsection{Professional Service}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Feb 2025 - current} & \textbf{Member} \\
& \textbf{America’s Network for Chronic Disease Surveillance (AMNET)} \\
& Regional organization that promotes chronic disease monitoring, knowledge implementation, and public health capacity building throughout the Americas. AMNET fosters collaboration between governmental and non-governmental entities to improve health professional training in disease surveillance, prevention, and control. \\
& \\
\textbf{Jan 2025 - current} & \textbf{Trainee Advisory Committee Member} \\
& \textbf{Consortium of Universities for Global Health, USA} \\
& Collaborating with international co-trainees to address global health challenges and provide student perspectives on global health issues such as COVID-19, racial disparities, climate change, and research involvement of global health students. \\
& \\
\textbf{Mar 2014 - current} & \textbf{Emeritus member and External advisor} \\
& \textbf{\href{https://cem.edu.pe/adiecs/}{Association for the Development of Student's Research in Health Sciences (ADIECS)}, Lima - Peru} \\
& Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos to develop capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students. \\
\end{longtable}

\subsection{Mentoring}
\subsubsection{Undergraduate thesis}
```{r}
#| name: mentees
mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```

```{r}
#| results: asis
#| name: mentees_table
mentees |> 
  filter(complete == 0) |>
  make_ordered_list_filtered("ug")
```

```{r}
#| results: asis
#| name: dumping_text
#| include: false
#| eval: false

\textbf{Clinical Sub-investigator} & \textbf{Mar 2022 - Mar 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{Via Libre Association}} \\
\multicolumn{2}{p{18cm}}{\textbf{Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Recruited patients identified as queer for clinical studies in STI and HIV prevention and treatment.
\item Performed clinical procedures and activities associated with the normal operation of clinical trials funded by NIH and pharmaceutical companies.
\item Participated and organized activities for community outreach and participant retention crafted for the queer community.
\end{itemize}
} \\

```
