---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 8pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\underline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.20\textwidth}
\faLinkedin \centering\href{https://www.linkedin.com/in/darwin-del-castillo/}{\hspace{0.5em}darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.20\textwidth}
\faEnvelope \centering\href{mailto:ddelcastillo.f@gmail.com}{\hspace{0.5em}ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.15\textwidth}
\faGithub \centering\href{https://github.com/ddelcastillof}{\hspace{0.5em}ddelcastillof} 
\end{minipage}
\vspace{-2.5pt}
\end{center}

```{r brief bio, eval = FALSE, include = FALSE, echo = FALSE}
\section{\underline{Summary}}
\justifying{Medical doctor and global health scientist with extensive experience bridging the gap between epidemiological methods and healthcare data science. I am committed to transforming early-life health outcomes through innovative research and data-driven solutions. I have collaborated with a diversity of global health institutions and managing research teams that translates data findings into actionable public health information.}
```
\section{Scientific Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textbf{University of Washington, Seattle - USA} & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textbf{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\end{longtable}

\section{Skills}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{minipage}[c]{0.65\textwidth}
Health data science and epidemiology: data wrangling, querying, analysis, visualization \& management
\vspace{1pt}
\begin{itemize}
\item SQL (MySQL), Python, R programming
\item HPC (Slurm), Linux environments (bash)
\item VS Code, Jupyter Lab, Quarto, Markdown, \LaTeX, Shiny (R), GIS tools
\item Team-based projects on Github and Bitbucket repositories
\item Packages: tidyverse, ggplot2, meta/metafor, lme4, survival, geepack, gam, lavaan, sf, rJAGS, rstan, Pandas, Matplotlib, NumPy, MR-BRT (GBD Study estimation), amongst other tools.
\end{itemize}
\end{minipage}
\begin{minipage}[c]{0.35\textwidth}
\begin{itemize}
\item Fluency in English \& Spanish
\item Team work \& collaboration
\item Problem solving
\item Science communication
\item Mentorship
\end{itemize}
\end{minipage}

\section{Professional Experience}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\multicolumn{2}{p{18cm}}{\textbf{Institute for Health Metrics and Evaluation}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Modeled epidemiological data on lower respiratory tract infections due to human metapneumovirus from 2010 to 2023 using meta-analysis information as priors and Bayesian meta-regression suites (DisMod-MR) in R.
\item Analyzed data from public sources using Bayesian methods and Monte Carlo simulation to estimate the proportion of overlap between socially excluded groups in high-income countries with the rJAGS and rstan packages.
\item Improved analytic scripts for electronic health records data extraction, cleaning, and analysis by developing Python functions that reduced processing time in high-performance computing contexts.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 – Mar 2025} \\
\multicolumn{2}{p{18cm}}{\textbf{Department of Global Health}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Synthesized clinical and research evidence into a scoping review to support the creation of indicators to guide mental health policy.
\item Designed a mixed-method study protocol to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting.
\item Crafted communication strategies with stakeholders to inform results from the mixed-methods study.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 – Mar 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Population Research Center}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Gathered sociodemographic and utlization data as part of a clinical trial post-assesment survey.
\item Translated IRB submission materials from Spanish to English for the Alzheimer’s Disease Research Center.
\item Synthesized early engagement and outreach data into visualisation tools and summary tables, enabling program managers to make adjustments to recruitment strategies.
\end{itemize}
} \\
\\
\textbf{RWE Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Technology Assessment and Research Institute}} \\
\multicolumn{2}{p{18cm}}{\textbf{Social Security Health System, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Structured and consolidated multi-source health data (surveillance data, clinical studies) to generate data for health technology assessments.
\item Conducted budget impact and cost-effectiveness analysis to prioritize funding for high-impact health interventions under national budgets.
\item Presented data-driven recommendations and evidence summaries to policymakers and partners, supporting strategic purchasing decisions for the Social Security System.
\end{itemize}
} \\
\newpage

\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{CRONICAS Center of Excellence in Chronic Diseases}} \\
\multicolumn{2}{p{18cm}}{\textbf{Universidad Peruana Cayetano Heredia, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Performed data curation, wrangling, and harmonization for multiple longitudinal cohort studies, processing complex datasets with 8+ years of follow-up data using R and SQL to ensure data integrity, standardization across multiple collection waves, and timely access for interdisciplinary research teams.
\item Conducted real-world evidence synthesis and preliminary data analyses to support grant proposals for hypertension, diabetes, cancer, and multimorbidity studies.
\item Co-authored peer-reviewed manuscripts as part of international collaborations, communicating complex analytical findings for academic and lay audiences.
\end{itemize}
} \\
\end{longtable}

\section{Additional Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

```{r teaching, eval = FALSE, include = FALSE, echo = FALSE}
\section{\underline{Teaching Experience}}
\subsection{Courses taught at the college level}
\subsubsection{Courses taught at Universidad Nacional Mayor de San Marcos}

df <- get_cv_sheet('classes') |> filter(univ == "UNMSM") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type,
      semester = ifelse(semester == 'Aut20', 'Aut20', semester)
    ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center")

\subsubsection{Courses taught at University of Washington}

df <- get_cv_sheet('classes') |> filter(univ == "UW") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type, 
      semester = ifelse(semester == 'Spr24', 'Spr24', semester)
      ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center")

\subsection{Other teaching experience}
teaching <- get_cv_sheet('teaching') |>
  arrange(desc(date)) |> 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    url = ifelse(is.na(url), NA, markdown_url(url)),
    date = ifelse(is.na(url), date, paste0(date, '. ', url)), 
    citation = paste(title, host, location, date, sep = '. ')
  )

\subsubsection{Seminars}

#| results: asis
make_ordered_list_filtered(teaching, "seminar")

\section{\underline{Advising}}
```

```{r}
#| include: false
#| eval: false
#| echo: false
#| name: skills_old

\section{\underline{Skills}}

\begin{justify}
\textbf{Computer and programming skills:} 
\begin{itemize}
\item \textbf{Programming \& Scripting} R, Python, bash
\item \textbf{Statistical \& Analytical Software:} Stata, SPSS
\item \textbf{Data Visualization \& GIS:} Shiny, ArcGIS
\item \textbf{Databases \& Query Languages:} SQL (MySQL)
\item \textbf{Version Control \& DevOps:} Git, GitHub, Bitbucket, Docker
\item \textbf{Development Environments:}: RStudio, VS Code, Jupyter Notebooks
\item \textbf{Operating Systems \& Platforms:} Linux/Unix, Windows (SSH)
\item \textbf{Documentation \& Collaboration:} LaTeX, Markdown, Confluence
\end{itemize}

\textbf{Languages:} 
\begin{longtable}{>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}}
English: Fluent & Spanish: Native & Portuguese: Working proficiency
\end{longtable}
\end{justify}
```



```{r}
#| name: leadership
#| include: false
#| eval: false
\section{\underline{Leadership and Service}}
\subsection{Professional Service}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Feb 2025 - current} & \textbf{Member} \\
& \textbf{America’s Network for Chronic Disease Surveillance (AMNET)} \\
& Regional organization that promotes chronic disease monitoring, knowledge implementation, and public health capacity building throughout the Americas. AMNET fosters collaboration between governmental and non-governmental entities to improve health professional training in disease surveillance, prevention, and control. \\
& \\
\textbf{Jan 2025 - current} & \textbf{Trainee Advisory Committee Member} \\
& \textbf{Consortium of Universities for Global Health, USA} \\
& Collaborating with international co-trainees to address global health challenges and provide student perspectives on global health issues such as COVID-19, racial disparities, climate change, and research involvement of global health students. \\
& \\
\textbf{Mar 2014 - current} & \textbf{Emeritus member and External advisor} \\
& \textbf{\href{https://cem.edu.pe/adiecs/}{Association for the Development of Student's Research in Health Sciences (ADIECS)}, Lima - Peru} \\
& Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos to develop capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students. \\
\end{longtable}

\section{Memberships}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{itemize}
 \item International Epidemiological Association (2020 - Current)
 \item Peruvian College of Physicians (2021 - Current)
 \item Consortium of Universities for Global Health (2023 - Current)
 \item America’s Network for Chronic Disease Surveillance (2025 - Current)
\end{itemize}
```

```{r}
#| name: mentees
#| include: false
#| eval: false

\subsection{Mentoring}
\subsubsection{Undergraduate thesis}

mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```

```{r}
#| results: asis
#| name: dumping_text
#| include: false
#| eval: false

\textbf{Clinical Sub-investigator} & \textbf{Mar 2022 - Mar 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{Via Libre Association}} \\
\multicolumn{2}{p{18cm}}{\textbf{Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Recruited patients identified as queer for clinical studies in STI and HIV prevention and treatment.
\item Performed clinical procedures and activities associated with the normal operation of clinical trials funded by NIH and pharmaceutical companies.
\item Participated and organized activities for community outreach and participant retention crafted for the queer community.
\end{itemize}
}
```
\section{Other Professional Activities}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\subsection{Teaching}
\vspace{-1em}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Mar 2025 – current} & \textbf{Lecturer: Introduction to Epidemiology.} Universidad Científica del Sur. I teach three sections of \textasciitilde 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts. \\
\textbf{Mar 2024 – Jun 2024} & \textbf{Teaching Assistant: Introduction to Molecular and Cellular Biology.} University of Washington. Led two laboratory practice sessions with \textasciitilde 25 undergraduate students each, covering fundamental molecular and cellular biology experiments. \\
\end{longtable}
\vspace{-0.75em}
\subsection{Mentoring}
\vspace{-0.75em}
\subsubsection{Undergraduate thesis}
\vspace{-0.75em}
```{r}
#| results: asis
#| name: mentees_table
mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
mentees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0(journal_abbv)),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```