---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 8pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\Large{\textbf{Darwin Del Castillo, MD, MPH}}
\end{center}
\vspace{-2.5pt}
\begin{minipage}[c]{0.65\textwidth}
\begin{itemize}
\item \textbf{Languages:} English (proficient), Spanish (native)
\item \textbf{Programming languages:} R, Python, SQL (MySQL), bash
\item \textbf{Other:} Linux/Unix, HPC (Slurm), \LaTeX, Markdown, VSCode, Jupyter Notebooks, Quarto, Docker, Git, Shiny (R), REDCap, ArcGIS
\end{itemize}
\end{minipage}
\begin{minipage}[c]{0.3\textwidth}
\centering
\faLinkedin \href{https://www.linkedin.com/in/darwin-del-castillo-md/}{/darwin-del-castillo} \\ 
\faGithub \href{https://github.com/ddelcastillof}{/ddelcastillof} \\
\faEnvelope \href{mailto:ddelcastillo.f@gmail.com}{/ddelcastillo.f@gmail.com}
\end{minipage}
\vspace{-2.5pt}

```{r brief bio, eval = FALSE, include = FALSE, echo = FALSE}
\section{\underline{Summary}}
\justifying{Medical doctor and global health scientist with extensive experience bridging the gap between epidemiological methods and healthcare data science. I am committed to transforming early-life health outcomes through innovative research and data-driven solutions. I have collaborated with a diversity of global health institutions and managing research teams that translates data findings into actionable public health information.}
```
\section{Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master in Public Health (MPH)} & \textbf{Sep 2023 – May 2025} \\
\textbf{University of Washington, Seattle - USA} & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textbf{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\end{longtable}

\section{Professional Experience}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 - Current} \\
\multicolumn{2}{p{18cm}}{\textbf{Institute for Health Metrics and Evaluation}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Conducted a comprehensive meta-analysis of lower respiratory tract infection rates across 80 countries using the R meta package, then applied Bayesian regressions to model epidemiological measures
\item Developed and executed Bayesian MCMC workflows to quantify the overlap among homeless populations, substance users, and incarcerated individuals across 22 high-income countries, producing real-world evidence for targeted health burden stratification.
\item Updated version-controlled scripts to automate data quality checks of EHR datasets from Ecuador and Colombia. 
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 - Mar 2025} \\
\multicolumn{2}{p{18cm}}{\textbf{Department of Global Health}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Synthesized clinical and research evidence into actionable insights and reports to support evidence-based policy and program decisions regarding mental health.
\item Analyzed pediatric clinical and outcome data to evaluate effectiveness of burn injury interventions and guide improvements in care protocols.
\item Engaged with Ministry of Health officials and hospital stakeholders to align pediatric burn care strategies with national healthcare priorities.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 - Mar 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Population Research Center}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Implemented standardized remote data-collection workflows to capture patient-reported outcomes.
\item Managed full lifecycle of IRB submissions—including translation and localization of Spanish-language documents—for the Alzheimer’s Disease Research Center, ensuring compliance with regulatory requirements.
\item Synthesized early engagement and outreach data into interactive dashboards and concise summary reports, enabling program managers to make timely adjustments to recruitment strategies.
\end{itemize}
} \\
\\
\textbf{RWE Consultant} & \textbf{Jan 2023 - Jan 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Technology Assessment and Research Institute}} \\
\multicolumn{2}{p{18cm}}{\textbf{Social Security Health System, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Structured and consolidated multi-source health data (surveillance, clinical studies) to provide comprehensive insights into healthcare outcomes.
\item Conducted budget impact and cost-effectiveness assessments to prioritize funding for high-impact health interventions under national budgets.
\item Presented data-driven recommendations and evidence summaries to policymakers and partners, supporting strategic purchasing decisions.
\end{itemize}
} \\
\\
\textbf{Research Assistant} & \textbf{Mar 2019 - Aug 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{CRONICAS Center of Excellence in Chronic Diseases}} \\
\multicolumn{2}{p{18cm}}{\textbf{Universidad Peruana Cayetano Heredia, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Led stakeholder workshops and focus groups across four regions to co-design patient-centered interventions, translating qualitative insights into quantifiable outcome metrics.
\item Conducted real-world evidence synthesis and preliminary data analyses to support grant proposals for hypertension, diabetes, and multimorbidity studies, informing funding decisions.
\item Co-authored peer-reviewed manuscripts and technical reports, communicating complex analytical findings in clear, executive-ready summaries for academic and policy audiences.
\end{itemize}
} \\

\newpage

\end{longtable}

\section{Additional Education}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

```{r teaching, eval = FALSE, include = FALSE, echo = FALSE}
\section{\underline{Teaching Experience}}
\subsection{Courses taught at the college level}
\subsubsection{Courses taught at Universidad Nacional Mayor de San Marcos}

df <- get_cv_sheet('classes') |> filter(univ == "UNMSM") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type,
      semester = ifelse(semester == 'Aut20', 'Aut20', semester)
    ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center")

\subsubsection{Courses taught at University of Washington}

df <- get_cv_sheet('classes') |> filter(univ == "UW") |>
    mutate(
      course = paste0(number, ": ", name),
      role = type, 
      semester = ifelse(semester == 'Spr24', 'Spr24', semester)
      ) |> 
    select(
      `Sem.` = semester,
      Course = course,
      Role = role,
      Level = level
    ) 

df |> 
  kbl(booktabs = TRUE, escape = FALSE, linesep = "") |>
  kable_styling(position = "center")

\subsection{Other teaching experience}
teaching <- get_cv_sheet('teaching') |>
  arrange(desc(date)) |> 
  mutate(
    with = ifelse(is.na(with), '', paste0(', with ', with)),
    title = paste0(enquote(title), with),
    date = paste0(format(as.Date(date), format = "%b %d, %Y"), '.'),
    url = ifelse(is.na(url), NA, markdown_url(url)),
    date = ifelse(is.na(url), date, paste0(date, '. ', url)), 
    citation = paste(title, host, location, date, sep = '. ')
  )

\subsubsection{Seminars}

#| results: asis
make_ordered_list_filtered(teaching, "seminar")

\section{\underline{Advising}}
```

```{r}
#| include: false
#| eval: false
#| echo: false
#| name: skills_old

\section{\underline{Skills}}

\begin{justify}
\textbf{Computer and programming skills:} 
\begin{itemize}
\item \textbf{Programming \& Scripting} R, Python, bash
\item \textbf{Statistical \& Analytical Software:} Stata, SPSS
\item \textbf{Data Visualization \& GIS:} Shiny, ArcGIS
\item \textbf{Databases \& Query Languages:} SQL (MySQL)
\item \textbf{Version Control \& DevOps:} Git, GitHub, Bitbucket, Docker
\item \textbf{Development Environments:}: RStudio, VS Code, Jupyter Notebooks
\item \textbf{Operating Systems \& Platforms:} Linux/Unix, Windows (SSH)
\item \textbf{Documentation \& Collaboration:} LaTeX, Markdown, Confluence
\end{itemize}

\textbf{Languages:} 
\begin{longtable}{>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}>{\centering\arraybackslash}p{6cm}}
English: Fluent & Spanish: Native & Portuguese: Working proficiency
\end{longtable}
\end{justify}
```

\section{Publications \hspace{1cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') %>%
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0(journal_abbv)),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    citation = paste(author, year, title, journal, number, doi)
  ) %>% 
  arrange(desc(pub_date))
```

```{r printing references in pandoc format}
#| results: asis
make_ordered_list_filtered(pubs, "peer_reviewed")
```

```{r}
#| name: leadership
#| include: false
#| eval: false
\section{\underline{Leadership and Service}}
\subsection{Professional Service}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Feb 2025 - current} & \textbf{Member} \\
& \textbf{America’s Network for Chronic Disease Surveillance (AMNET)} \\
& Regional organization that promotes chronic disease monitoring, knowledge implementation, and public health capacity building throughout the Americas. AMNET fosters collaboration between governmental and non-governmental entities to improve health professional training in disease surveillance, prevention, and control. \\
& \\
\textbf{Jan 2025 - current} & \textbf{Trainee Advisory Committee Member} \\
& \textbf{Consortium of Universities for Global Health, USA} \\
& Collaborating with international co-trainees to address global health challenges and provide student perspectives on global health issues such as COVID-19, racial disparities, climate change, and research involvement of global health students. \\
& \\
\textbf{Mar 2014 - current} & \textbf{Emeritus member and External advisor} \\
& \textbf{\href{https://cem.edu.pe/adiecs/}{Association for the Development of Student's Research in Health Sciences (ADIECS)}, Lima - Peru} \\
& Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos to develop capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students. \\
\end{longtable}
```

```{r}
#| name: mentees
#| include: false
#| eval: false

\subsection{Mentoring}
\subsubsection{Undergraduate thesis}

mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
```

```{r}
#| results: asis
#| name: mentees_table
#| include: false
#| eval: false
mentees |> 
  filter(complete == 0) |>
  make_ordered_list_filtered("ug")
```

```{r}
#| results: asis
#| name: dumping_text
#| include: false
#| eval: false

\textbf{Clinical Sub-investigator} & \textbf{Mar 2022 - Mar 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{Via Libre Association}} \\
\multicolumn{2}{p{18cm}}{\textbf{Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Recruited patients identified as queer for clinical studies in STI and HIV prevention and treatment.
\item Performed clinical procedures and activities associated with the normal operation of clinical trials funded by NIH and pharmaceutical companies.
\item Participated and organized activities for community outreach and participant retention crafted for the queer community.
\end{itemize}
} \\

```

\section{Other activities}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Jan 2025 - current} & \textbf{Lecturer: Introduction to Epidemiology.} Universidad Científica del Sur. I'm teaching fourth-year medical students basic concepts of clinical epidemiology with focus in basic study designs and identification of bias.
\end{longtable}

\section{Memberships}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{itemize}
 \item International Epidemiological Association (2020 - Current)
 \item Peruvian College of Physicians (2021 - Current)
 \item Consortium of Universities for Global Health (2023 - Current)
 \item America’s Network for Chronic Disease Surveillance (2025 - Current)
\end{itemize}