---
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\underline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.20\textwidth}
\faLinkedin \centering\href{https://www.linkedin.com/in/darwin-del-castillo/}{\hspace{0.5em}darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.25\textwidth}
\faEnvelope \centering\href{mailto:ddelcastillo.f@gmail.com}{\hspace{0.5em}ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.15\textwidth}
\faGithub \centering\href{https://github.com/ddelcastillof}{\hspace{0.5em}ddelcastillof} 
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Scientific Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, Seattle - USA} & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
Broad experience in the health data lifecycle: data collection, management, wrangling, querying, analysis, \& visualization.
\begin{minipage}[c]{0.70\textwidth}
\vspace{1pt}
\begin{itemize}
\item SQL (MySQL), Python, R, Stata
\item Machine learning: PyTorch, TensorFlow/Keras, scikit‑learn; basic self‑supervised and probabilistic methods
\item Data engineering and pipelines: Apache Spark/PySpark, Airflow, dbt, Pandas
\item Cloud \& compute: AWS SageMaker, Docker, Slurm HPC, CUDA
\item Experiment tracking: MLflow, Weights \& Biases
\item Wearable \& CGM signal processing: HeartPy, NeuroKit2, SciPy; \texttt{cgmanalysis} (R), \texttt{cgmquantify} (Python)
\item Data standards: HIPAA, HL7 FHIR, GDPR / UK GDPR + DPA 2018
\item Tools: VS Code, Jupyter, Quarto, \LaTeX; Git version control
\end{itemize}
\end{minipage}
\begin{minipage}[c]{0.30\textwidth}
\begin{itemize}
\item Fluency in English \& Spanish
\item Teamwork \& collaboration
\item Problem solving
\item Science communication
\item Mentorship
\end{itemize}
\end{minipage}

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 - Jun 2025} \\
\multicolumn{2}{p{18cm}}{\textbf{Institute for Health Metrics and Evaluation}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Conducted a comprehensive meta-analysis of lower respiratory tract infection rates across 80 countries using the R meta package to support strategic program planning; presented findings with ROI-style visual summaries to senior leadership.
\item Developed and executed Bayesian MCMC workflows to quantify the overlap among homeless populations, substance users, and incarcerated individuals across 22 high-income countries, producing real-world evidence for targeted health burden stratification.
\item Updated version-controlled scripts to automate data quality checks of EHR datasets from Ecuador and Colombia; identified root causes of data anomalies, reducing error rates by 23% and improving data reliability across 30 million records. 
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 - Mar 2025} \\
\multicolumn{2}{p{18cm}}{\textbf{Department of Global Health}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Synthesized clinical and programmatic evidence into actionable insights and reports to support program design and policy decisions in mental health.
\item Analyzed pediatric clinical and outcome data to evaluate effectiveness of burn injury interventions; compiled initiative-level monthly performance reports for Ministry of Health and hospital leadership to inform protocol refinements.
\item Engaged with Ministry of Health officials and hospital stakeholders to align pediatric burn care strategies with national healthcare priorities.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 - Mar 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Population Research Center}} \\
\multicolumn{2}{p{18cm}}{\textbf{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Implemented standardized remote data-collection workflows to capture patient-reported outcomes.
\item Managed full lifecycle of IRB submissions—including translation and localization of Spanish-language documents—for the Alzheimer’s Disease Research Center, ensuring compliance with regulatory requirements.
\item Synthesized weekly/monthly engagement and outreach data into interactive Shiny dashboards and concise summary reports for program managers and stakeholders, enabling timely strategic recruitment adjustments.
\end{itemize}
} \\
\\
\textbf{RWE Consultant} & \textbf{Jan 2023 - Jan 2024} \\
\multicolumn{2}{p{18cm}}{\textbf{Health Technology Assessment and Research Institute}} \\
\multicolumn{2}{p{18cm}}{\textbf{Social Security Health System, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Structured and consolidated multi-source health data (surveillance, clinical studies) to provide comprehensive insights into healthcare outcomes.
\item Conducted budget impact and cost-effectiveness assessments to prioritize funding for high-impact health interventions under national budgets.
\item Presented data-driven recommendations and evidence summaries to policymakers and partners, supporting strategic purchasing decisions.
\end{itemize}
} \\
\\
\textbf{Research Assistant} & \textbf{Mar 2019 - Aug 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{CRONICAS Center of Excellence in Chronic Diseases}} \\
\multicolumn{2}{p{18cm}}{\textbf{Universidad Peruana Cayetano Heredia, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Led stakeholder workshops and focus groups across four regions to co-design patient-centered interventions, translating qualitative insights into quantifiable outcome metrics.
\item Conducted real-world evidence synthesis and preliminary data analyses to support program proposals in hypertension, diabetes, and multimorbidity, informing strategic funding decisions.
\item Co-authored evidence summaries and reports, translating analytical findings into executive-ready deliverables for program managers and health policy audiences.
\end{itemize}
} \\

\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

```{r}
#| name: leadership
#| include: false
#| eval: false
\section{\underline{Leadership and Service}}
\subsection{Professional Service}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Feb 2025 - current} & \textbf{Member} \\
& \textbf{America’s Network for Chronic Disease Surveillance (AMNET)} \\
& Regional organization that promotes chronic disease monitoring, knowledge implementation, and public health capacity building throughout the Americas. AMNET fosters collaboration between governmental and non-governmental entities to improve health professional training in disease surveillance, prevention, and control. \\
& \\
\textbf{Jan 2025 - current} & \textbf{Trainee Advisory Committee Member} \\
& \textbf{Consortium of Universities for Global Health, USA} \\
& Collaborating with international co-trainees to address global health challenges and provide student perspectives on global health issues such as COVID-19, racial disparities, climate change, and research involvement of global health students. \\
& \\
\textbf{Mar 2014 - current} & \textbf{Emeritus member and External advisor} \\
& \textbf{\href{https://cem.edu.pe/adiecs/}{Association for the Development of Student Research in Health Sciences (ADIECS)}, Lima - Peru} \\
& Peruvian student association funded in 2008 by students from the Universidad Nacional Mayor de San Marcos to develop capacity of both hard (e.g., epidemiological study designs, data analysis) and soft skills (e.g., teamwork communication, problem-solving) for biomedical underserved students. \\
\end{longtable}

\section{Memberships}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{itemize}
 \item International Epidemiological Association (2020 - Current)
 \item Peruvian College of Physicians (2021 - Current)
 \item Consortium of Universities for Global Health (2023 - Current)
 \item America’s Network for Chronic Disease Surveillance (2025 - Current)
\end{itemize}
```

```{r}
#| results: asis
#| name: dumping_text
#| include: false
#| eval: false

\textbf{Clinical Sub-investigator} & \textbf{Mar 2022 - Mar 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{Via Libre Association}} \\
\multicolumn{2}{p{18cm}}{\textbf{Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Recruited patients identified as queer for clinical studies in STI and HIV prevention and treatment.
\item Performed clinical procedures and activities associated with the normal operation of clinical trials funded by NIH and pharmaceutical companies.
\item Participated and organized activities for community outreach and participant retention crafted for the queer community.
\end{itemize}
} \\

```

\section*{Teaching Professional Activities}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Teaching}
\vspace{-1em}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Mar 2025 – current} & \textbf{Lecturer: Introduction to Epidemiology.} \textsc{Universidad Científica del Sur}. I teach three sections of \textasciitilde{} 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts. \\
\textbf{Mar 2024 – Jun 2024} & \textbf{Teaching Assistant: Introduction to Molecular and Cellular Biology.} \textsc{University of Washington}. Led two laboratory practice sessions with \textasciitilde{} 25 undergraduate students each, covering fundamental molecular and cellular biology experiments. \\
\end{longtable}
\vspace{-0.75em}
\subsection{Mentoring}
\vspace{-0.75em}
\subsubsection{Undergraduate thesis}
\vspace{-0.75em}
```{r}
#| results: asis
#| name: mentees_table
mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
mentees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(pub_date))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```