---
format:
  pdf:
    output-file: delcastillo_darwin_cv.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\Large{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Scientific Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH) – Epidemiology} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, Seattle - USA} & \\

&\\

\textbf{Doctor of Medicine (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Lima - Peru} & \\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\textbf{Programming:} R, Stata, SQL (MySQL), Python \
\textbf{Cloud Computing:} Slurm HPC, Docker, Linux environments (bash) \
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Shiny (R), ArcGIS, Power BI, Git version control (GitHub, Bitbucket, GitLab), REDCap \
\textbf{Data Standards:} HIPAA, ICH E6, HL7 FHIR, GDPR, UK GDPR, DPA 2018, OMOP CDM, ICD-10/ICD-9/SNOMED \
\textbf{Packages:} \texttt{tidyverse}, \texttt{data.table}, \texttt{ggplot2}, \texttt{lme4}, \texttt{survival}, \texttt{sf}, \texttt{cmprsk}, \texttt{mice}, \texttt{geepack}, \texttt{metafor}, \texttt{rstan}, \texttt{caret}, \texttt{ivreg}, \texttt{Pandas}, \texttt{NumPy}, \texttt{Matplotlib}, MR-BRT \
\textbf{Statistical methods:} Bayesian hierarchical modelling (MCMC), GLM/GLMM, time-to-event models, propensity score matching, marginal structural models, competing risks, multiple imputation, meta-analysis, crosswalking, uncertainty quantification (confidence \& posterior intervals) \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{UW Medicine Diabetes Institute} & \textbf{Seattle - USA} \\
\textbf{Research Scientist} & \textbf{Mar 2025 – Current} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Developed advanced survival analyses and omics integration pipelines to identify early biomarkers of diabetic complications, accelerating precision medicine approaches for youth-onset type 2 diabetes patient stratification.
  \item Engineered scalable data integration platform harmonizing multimodal datasets from 10 clinical studies, enabling cross-study meta-analyses and improving statistical power for biomarker discovery.
  \item Built data visualization dashboards supporting real-time clinical decision support, enhancing research team productivity and enabling rapid hypothesis testing across metabolomic profiles.
\end{itemize}
} \\
\\
\textbf{Institute for Health Metrics and Evaluation} & \textbf{Seattle - USA} \\
\textbf{Graduate Research Assistant} &  \textbf{Jul 2024 – Jun 2025} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Led population health analyses across 22 countries using real-world datasets, generating evidence-based insights for strategic decision-making and market access optimization.
  \item Developed Bayesian statistical models to define patient phenotypes and estimate disease burden, directly supporting epidemiological research critical for pharmaceutical target identification and indication expansion.
  \item Built production-grade data quality pipelines processing 30+ million EHR records, ensuring data integrity standards essential for regulatory submissions and post-market surveillance.
\end{itemize}
} \\
\\
\textbf{Health Technology Assessment and Research Institute} & \textbf{Lima - Peru} \\
\textbf{Real-World-Evidence Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Generated real-world evidence from claims and inpatient data to support market access strategies and value demonstration for chronic disease therapeutics.
  \item Performed health economic evaluations including budget impact and cost-effectiveness analyses, directly informing pricing strategies and reimbursement negotiations with payers.
  \item Delivered evidence synthesis and strategic recommendations to stakeholders, translating complex clinical data into actionable insights for commercial and regulatory teams.
\end{itemize}
} \\
\newpage
\textbf{CRONICAS Center of Excellence in Chronic Diseases} & \textbf{Lima - Peru}\\
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Designed patient-centered intervention studies through stakeholder engagement, developing clinically meaningful endpoints for cardiometabolic disease research aligned with regulatory requirements.
  \item Conducted longitudinal cohort studies in diabetes, hypertension, and multimorbidity, generating real-world evidence to support indication expansion and clinical development programs.
  \item Authored scientific communications and regulatory documents, demonstrating ability to translate complex clinical data into clear narratives for diverse audiences including regulatory agencies.
\end{itemize}
} \\

\end{longtable}
\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
                ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(year))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```