---
format:
  pdf:
    output-file: delcastillo_darwin_cv.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\Large{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Scientific Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH) – Epidemiology} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, Seattle - USA} & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Lima - Peru} & \\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\textbf{Programming:} SQL (MySQL), Python, R, Stata, C++ \
\textbf{Cloud Computing:}  HPC (Slurm), Linux environments (bash) \
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Git version control \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship \
\textbf{Packages:} \emph{R} (tidyverse, ggplot2, rJAGS, rstan, SummarizedExperiment, MultiAssayExperiment, GenomicRanges, biomaRt, VariantAnnotation, SNPRelate, mixOmics, xcms, MSnbase, CAMERA, sva/ComBat EnhancedVolcano); \emph{Python} (Pandas, Matplotlib, NumPy, scikit-allel, pysam, pybedtools). \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{UW Medicine Diabetes Institute} & \textbf{Seattle - USA} \\
\textbf{Research Scientist} & \textbf{Sep 2024 – Current} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Conduct longitudinal metabolomics analyses for the TODAY and TODAY2 cohorts, leveraging \textasciitilde 10 years of follow-up in youth-onset type 2 diabetes to model metabolite trajectories and cardiometabolic disease progression.
  \item Define and operationalise cardio-kidney-metabolic (CKM) syndrome progression categories as clinical outcomes into the TODAY samples, quantifying associations with metabolite using mixed-effects and multinomial/ordinal models.
  \item Lead a cross-cohort multi-omics analysis across ARIC, UK Biobank, PURE Latin America, and HELIUS to estimate associations between CKM syndrome and omic features.
  \item Specify clinically relevant phenotypes for obesity- and liver-related metabolic disease and design association analyses in large cohorts (e.g., UK Biobank).
  \item Build reproducible R/Python workflows on HPC (Slurm/Linux) for data cleaning, batch correction, feature engineering, multiple-testing control, and sensitivity analyses, producing publication-ready figures and tables.
\end{itemize}
} \\
\\
\textbf{Institute for Health Metrics and Evaluation} & \textbf{Seattle - USA} \\
\textbf{Graduate Research Assistant} &  \textbf{Jul 2024 – Jun 2025} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Designed and led epidemiological studies using large-scale datasets; delivered medically relevant findings through country-comparative meta-analyses and decision-focused reports for leadership.
  \item Built Bayesian MCMC workflows to estimate overlap among inclusion-health populations across 22 high-income countries, informing phenotype definition and downstream burden estimation.
  \item Productionised version-controlled R pipelines for EHR data quality assessment (Git/HPC), diagnosing anomalies and improving reliability across \textasciitilde 30 million records.
\end{itemize}
} \\
\\
\textbf{Health Technology Assessment and Research Institute} & \textbf{Lima - Peru} \\
\textbf{Real-World-Evidence Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Structured and consolidated multi-source health data (surveillance, clinical studies) to generate real-world evidence for priority setting in chronic and cardiometabolic disease.
  \item Conducted budget impact and cost-effectiveness assessments to inform reimbursement and strategic purchasing decisions under national budgets.
  \item Synthesised evidence into executive-ready briefs for policymakers and clinical partners, emphasising quantitative strength of evidence and uncertainty.
\end{itemize}
} \\
\newpage
\textbf{CRONICAS Center of Excellence in Chronic Diseases} & \textbf{Lima - Peru}\\
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Led stakeholder workshops and focus groups to co-design patient-centred interventions; translated qualitative insights into measurable cardiometabolic outcomes.
  \item Conducted real-world evidence synthesis and cohort analyses in hypertension, diabetes, and multimorbidity, supporting grant proposals and programme design.
  \item Co-authored evidence summaries and reports for policy audiences, communicating complex analyses clearly to non-technical stakeholders.
\end{itemize}
} \\

\end{longtable}
\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
                ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(year))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```