---
format:
  pdf:
    output-file: delcastillo_darwin_resume.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r setup}
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Scientific Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH) – Epidemiology} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington} & \textsc{Seattle - USA} \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos} & \textsc{Lima - Peru} \\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\textbf{Programming:} SQL (MySQL), Python, R, Stata \
\textbf{Cloud Computing:}  HPC (Slurm), Linux environments (bash) \
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Shiny (R), REDCap, ArcGIS, Git (GitHub, Bitbucket) \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship \
\textbf{Packages:} \textbf{R} tidyverse, ggplot2, lme4, survival, geepack, gam, lavaan, sf (geospatial), rJAGS, rstan, meta/metafor, \textbf{Python} Pandas, NumPy, Matplotlib, MR-BRT (GBD Study estimation)

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\textbf{Institute for Health Metrics and Evaluation} & \textbf{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Developed Bayesian priors for a Bayesian hierarchical meta‑regression model to estimate prevalence, incidence, and clinical outcomes of lower‑respiratory‑tract infections across 80 countries, informing GBD 2025 inputs.
  \item Produced a global map of study locations from the GBD 2023 using R (sf) to visualize geographic coverage and data gaps, informing meta-analysis data sources.
  \item Executed a version-controlled (Git/GitHub) workflow to run a Gibbs sampler with data-driven priors to estimate the overlap among inclusion health populations in 22 high-income countries and to compute population-attributable fractions and standardized mortality ratios.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 – Mar 2025} \\
\textbf{Department of Global Health – University of Washington} & \textbf{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
  \item Designed the study protocol and coordinated a mixed-methods evaluation of implementation strategies for pediatric burn care across >10 low-resource Peruvian hospitals.
  \item Co-developed communication strategies with 2 stakeholder organizations to translate complex findings for healthcare policymakers.
  \item Prepared slide decks and briefings for stakeholder workshops and meetings.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 – Mar 2024} \\
\textbf{Health Population Research Center – University of Washington} & \textbf{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
  \item Maintained and stored sociodemographic and utilization data as part of a clinical trial post-assessment survey using electronic data capture platforms.
  \item Translated IRB submission materials from Spanish to English for the Alzheimer’s Disease Research Center.
  \item Analyzed engagement and outreach data and produced visualizations and summary tables, enabling program managers to adjust recruitment strategies.
\end{itemize}
} \\
\\
\textbf{Real World Evidence Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\textbf{Health Technology Assessment and Research Institute} & \textbf{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Integrated surveillance and clinical data from 80 Peruvian hospitals into statistical burden models to support national health technology assessment and prioritization processes.
  \item Conducted budget impact and cost-effectiveness analyses that prioritized oncological interventions worth \$1 M+.
  \item Synthesized findings into executive reports aimed at policymakers and partners, guiding reimbursement policy for Peru's Social Security System.
\end{itemize}
} \\
\newpage
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\textbf{CRONICAS Center of Excellence in Chronic Diseases} & \textbf{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Coordinated 2 workshops per site with community health workers in 3 Peruvian regions to co-design a mobile application for early detection of cognitive impairment and dementia.
  \item Conducted preliminary analyses on clinical and demographic data to inform proposals in cardiometabolic epidemiology, migration, and social determinants of health supporting \$300\,k in competitive funding.
  \item Co-authored 5 scientific manuscripts, including longitudinal analyses, systematic reviews, and machine-learning models, using existing data from the PERU MIGRANT and the CRONICAS cohort studies, among other datasets.
\end{itemize}
} \\
\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia} & \textsc{Lima - Peru} \\
\end{longtable}

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
       ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(year))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```