---
format:
  pdf:
    output-file: resume.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, Seattle - USA} & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\textbf{Programming:} SQL (MySQL), Python, R, Stata \
\textbf{Machine Learning:} PyTorch, TensorFlow/Keras, scikit-learn, self-supervised learning, probabilistic methods \
\textbf{Data Engineering:} Apache Spark/PySpark, Airflow, dbt, Pandas \
\textbf{Cloud Computing:} AWS SageMaker, Docker, Slurm HPC, CUDA \
\textbf{Experiment Tracking:} MLflow, Weights and Biases \
\textbf{Signal Processing:} HeartPy, NeuroKit2, SciPy, \texttt{RHRV}, \texttt{cgmanalysis} (R), \texttt{cgmquantify} (Python) \
\textbf{Data Standards:} HIPAA, HL7 FHIR, GDPR, UK GDPR, DPA 2018 \
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Git version control \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Institute for Health Metrics and Evaluation} & \textbf{Seattle, USA} \\
\textbf{Graduate Research Assistant} &  \textbf{Jul 2024 – Jun 2025} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Developed informative Bayesian priors and covariate structures for a Bayesian hierarchical meta‑regression model to estimate prevalence, incidence, and clinical‐outcome occurrence of lower‑respiratory‑tract infections across 80 countries, informing GBD 2025 inputs.
\item Executed LLM algorithms over EHR data to screen ICD-9 and ICD-10 codes for estimating mortality rates among homeless populations, substance users, and incarcerated individuals across 22 high-income countries, reducing processing time by 25\%.
\item Led ML workflows on EHR data extraction from 2 countries with 60+ million records to build population-level summaries per age and sex groups. 
\end{itemize}
} \\
\\
\textbf{University of Washington} & \textbf{Seattle, USA} \\
\textbf{Graduate Research Assistant} & \textbf{Sep 2023 – Jun 2024} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Partnered with clinicians, and project managers in Peru to translate burn-care evidence into prototype decision-support dashboards.
\item Analyzed Peruvian pediatric EHR data under HIPAA standards to evaluate burn-injury intervention outcomes with survival and causal inference models.
\item Presented findings to 15+ MoH officials and hospital stakeholders to align pediatric burn care strategies with national healthcare priorities, improving pediatric care for over 50\,000+ patients annually.
\end{itemize}
} \\
\\
\textbf{Health Technology Assessment and Research Institute} & \textbf{Lima, Peru} \\
\textbf{Real-World-Evidence Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Harmonized claims and inpatient EHR-data from \textgreater50 hospitals to provide comprehensive insights into healthcare outcomes.
\item Executed budget impact and cost-effectiveness models that prioritized oncological interventions worth \$1 M+.
\item Synthesised peer-reviewed literature and real-world evidence into executive reports, guiding reimbursement policy for Peru’s Social Security System.
\end{itemize}
} \\
\\
\textbf{Anglo-American Hospital} & \textbf{Lima, Peru}\\
\textbf{Resident Physician – Department of Pediatrics} & \textbf{Sep 2021 – Aug 2023}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Delivered clinical care for 500+ patients monthly in pediatric internal medicine and emergency rotations.
\item Carried out chart reviews and clinical assessments during sub-speciality rotations, evaluating diagnostic accuracy of auxiliary test interpretations and correlating findings with patient outcomes to improve clinical decision-making protocols.
\end{itemize}
} \\
\\
\textbf{CRONICAS Center of Excellence in Chronic Diseases} & \textbf{Lima, Peru}\\
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Coordinated a human-centered design study for cognitive impairment screening, co‑creating a mobile app with regional stakeholders and community health workers.
\item Processed continuous-glucose-monitoring and activity‑tracker data using RHRV and cgmanalysis, generating features for subsequent statistical models in diabetes trials.
\item Translated findings into executive briefs and grant proposals that secured \$300\,k in competitive funding.
\end{itemize}
}
\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textbf{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(pub_date))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```