---
format:
  pdf:
    output-file: resume.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\underline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.20\textwidth}
\faLinkedin \centering\href{https://www.linkedin.com/in/darwin-del-castillo/}{\hspace{0.5em}darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.25\textwidth}
\faEnvelope \centering\href{mailto:ddelcastillo.f@gmail.com}{\hspace{0.5em}ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.15\textwidth}
\faGithub \centering\href{https://github.com/ddelcastillof}{\hspace{0.5em}ddelcastillof} 
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Scientific Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, Seattle - USA} & \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
Broad experience in the health data lifecycle: data collection, management, wrangling, querying, analysis, \& visualization.
\begin{minipage}[c]{0.70\textwidth}
\vspace{1pt}
\begin{itemize}
\item SQL (MySQL), Python, R, Stata
\item HPC (Slurm), Linux environments (bash)
\item VS Code, Jupyter Notebook, Quarto, Markdown, \LaTeX, Shiny (R), GIS tools, REDCap
\item Team-based projects on Github and Bitbucket repositories
\item Packages: tidyverse, ggplot2, meta/metafor, lme4, survival, geepack, gam, lavaan, sf, rJAGS, rstan, Pandas, Matplotlib, NumPy, MR-BRT (GBD Study estimation), amongst other tools.
\end{itemize}
\end{minipage}
\begin{minipage}[c]{0.30\textwidth}
\begin{itemize}
\item Fluency in English \& Spanish
\item Teamwork \& collaboration
\item Problem solving
\item Science communication
\item Mentorship
\end{itemize}
\end{minipage}

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\multicolumn{2}{p{18cm}}{\textsc{Institute for Health Metrics and Evaluation}} \\
\multicolumn{2}{p{18cm}}{\textsc{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Modeled epidemiological data of lower respiratory tract infections due to human metapneumovirus from 2010 to 2023 using meta-analysis information in R and Bayesian meta-regression suites (DisMod-MR).
  \item Analyzed data from public sources using Bayesian methods and Monte Carlo simulation to estimate the overlap proportion between socially excluded groups in high-income countries using the packages rJAGS and rstan.
  \item Estimated population-attributable fractions and standardized mortality ratios for socially excluded groups in high-income countries.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 – Mar 2025} \\
\multicolumn{2}{p{18cm}}{\textsc{Department of Global Health}} \\
\multicolumn{2}{p{18cm}}{\textsc{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
  \item Conducted a scoping review protocol and performed evidence synthesis for mapping potential indicators for implementing mental health policy in data-limited settings.
  \item Designed of a mixed-method study protocol to assess the effectiveness of implementation strategies for pediatric burn care in a Peruvian healthcare setting.
  \item Crafted communication strategies with stakeholders to inform results from the mixed-methods study.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 – Mar 2024} \\
\multicolumn{2}{p{18cm}}{\textsc{Health Population Research Center}} \\
\multicolumn{2}{p{18cm}}{\textsc{University of Washington, Seattle (USA)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
  \item Gathered sociodemographic and utilization data as part of a clinical trial post-assesment survey through on-phone interviews.
  \item Translated IRB submissions materials from Spanish to English for the Alzheimer’s Disease Research Center.
  \item Synthesized early engagement and outreach data into visualisation tools and summary tables, enabling program managers to make adjustments to recruitment strategies.
\end{itemize}
} \\
\newpage
\textbf{RWE Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\multicolumn{2}{p{18cm}}{\textsc{Health Technology Assessment and Research Institute}} \\
\multicolumn{2}{p{18cm}}{\textsc{Social Security Health System, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
 \item Structured and consolidated multi-source health data (surveillance data, clinical studies) to generate data for health technology assessments.
  \item Conducted budget impact and cost-effectiveness assessments to prioritize funding for high-impact health interventions under national budgets.
  \item Presented data-driven recommendations and evidence summaries to policymakers and partners, supporting strategic purchasing decisions for the Social Security System.
\end{itemize}
} \\
\\
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\multicolumn{2}{p{18cm}}{\textsc{CRONICAS Center of Excellence in Chronic Diseases}} \\
\multicolumn{2}{p{18cm}}{\textsc{Universidad Peruana Cayetano Heredia, Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Coordinated focus groups and on-field work across four Peruvian regions to co-design an intervention for patients with cognitive impairment and their caregivers.
  \item Contributed to research grant proposals in hypertension, diabetes, cancer, and multimorbidity projects by conducting systematic reviews and preliminary data analysis.
  \item Co-authored scientific manuscripts in the topics mentioned above which included longitudinal data analyses, meta-analyses, and unsupervised machine learning methods.
\end{itemize}
} \\
\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia, Lima - Peru} &\\
\end{longtable}

\section*{Teaching Professional Activities}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Teaching}
\vspace{-1em}
\begin{longtable}{>{\raggedright\arraybackslash}p{4cm} p{14cm}}
\textbf{Mar 2025 – current} & \textbf{Lecturer: Introduction to Epidemiology.} \textsc{Universidad Científica del Sur}. I teach three sections of \textasciitilde{} 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts. \\
\textbf{Mar 2024 – Jun 2024} & \textbf{Teaching Assistant: Introduction to Molecular and Cellular Biology.} \textsc{University of Washington}. Led two laboratory practice sessions with \textasciitilde{} 25 undergraduate students each, covering fundamental molecular and cellular biology experiments. \\
\end{longtable}
\vspace{-0.75em}
\subsection{Mentoring}
\vspace{-0.75em}
\subsubsection{Undergraduate thesis}
\vspace{-0.75em}
```{r}
#| results: asis
#| name: mentees_table
mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
mentees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\end{longtable}

\newpage

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = ifelse(
               is.na(doi), '',
               paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(pub_date))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```