---
format:
  pdf:
    output-file: delcastillo_091725.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r setup}
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH) – Epidemiology} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington} & \textsc{Seattle - USA} \\

&\\

\textbf{Medical Doctor (MD)} & \textbf{Mar 2014 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos} & \textsc{Lima - Peru} \\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\textbf{Programming:} SQL (MySQL/PostgreSQL), Python, R, Stata \
\textbf{Cloud Computing:} Slurm HPC, Docker, Linux environments (bash) \
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Shiny (R), Git version control (GitHub, Bitbucket) \
\textbf{Data Standards:} HIPAA, HL7 FHIR, GDPR, UK GDPR, DPA 2018 \
\textbf{Packages:} \texttt{tidyverse}, Pandas, \texttt{ggplot2}, \texttt{lme4}, \texttt{mice}, \texttt{survival}, \texttt{geepack}, \texttt{gam}, \texttt{rJAGS}, \texttt{rstan}, \texttt{metafor}, \texttt{did}, NumPy, Matplotlib, Seaborn, MR-BRT (GBD Study estimation) \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Statistical methods:} Survival models, mixed models/GEE, multiple imputation, bootstrapping, interrupted time-series analysis, crosswalking, difference-in-differences analysis, joinpoint regression\
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\textsc{Institute for Health Metrics and Evaluation} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Led the development of hyperparameters for a Bayesian hierarchical meta‑regression model to estimate prevalence, incidence, and clinical outcomes of lower‑respiratory‑tract infections across 80 countries.
  \item Executed an MCMC algorithm with data-driven priors and uncertainty propagation to estimate the overlap among inclusion health populations in 22 high-income countries to compute population-attributable fractions and standardized mortality ratios.
  \item Performed ML algorithms on EHR data extraction from 2 countries with 60+ million records to build population-level summaries per age and sex groups, including simulation-based scenario testing.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Sep 2023 – Jun 2024} \\
\textsc{Department of Global Health – University of Washington} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
  \item Designed the study protocol and coordinated a mixed-methods evaluation of implementation strategies for pediatric burn care across >10 low-resource Peruvian hospitals.
  \item Co-developed communication strategies with 2 stakeholder organizations to translate complex findings for healthcare policymakers.
  \item Conducted a systematic review to assess mental health policy implementation indicators in low-and middle-income countries as part of a consultancy for an international NGO.
\end{itemize}
} \\
\\
\textbf{Real-World Evidence Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\textsc{Social Security System (ESSALUD)} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Harmonized claims and inpatient EHR data from +50 hospitals to provide comprehensive insights into healthcare outcomes.
  \item Executed budget impact and cost-effectiveness models that prioritized oncological interventions worth \$1 M+.
  \item Synthesised systematic review/evidence synthesis and statistical estimates from clinical data into executive reports, guiding reimbursement policy for Peru’s Social Security System.
\end{itemize}
} \\
\\
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\textsc{CRONICAS Center of Excellence in Chronic Diseases} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Analyzed longitudinal data from observational studies and RCTs using generalised linear methods and survival curves in cardiometabolic disease epidemiology. 
  \item Conducted preliminary data analysis on clinical, demographic, and biological biomarkers to support research grant proposals.
  \item Co-authored 5 scientific manuscripts, which included longitudinal data analyses and machine learning models.
\end{itemize}
} \\
\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia} & \textsc{Lima - Peru} \\
\end{longtable}

\section*{Research Support and Teaching Activities}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Research Support}
```{r importing grants, include = F, echo = F}
grants <- get_cv_sheet('grants') |>
  mutate(
    status  = na_to_space(status),
    role = na_to_space(role),
    project_code = na_to_space(id),
    budget   = na_to_space(budget_total),
    awarded   = na_to_space(awarded),
    funder_1 = na_to_space(sponsor_1),
    funder_2 = na_to_space(sponsor_2),
    year_start = na_to_space(begin),
    year_end = na_to_space(end),
    title = na_to_space(title),
    pi = ifelse(is.na(pi), '', paste0(pi, '.')),
    coi_1 = ifelse(is.na(coi_1), '', paste0(coi_1, '.')),
    coi_2 = ifelse(is.na(coi_2), '', paste0(coi_2, '.'))
    ) |> 
  arrange(desc(status))
```
\subsubsection{Concluded Research Support}
```{r grants_text}
#| results: asis
make_grants_table(grants, "concluded")
```

\subsection{Teaching}
\vspace{-1em}
\begin{longtable}{>{\raggedright\arraybackslash}p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Lecturer} & \textbf{Mar 2025 – Current} \\
\textsc{School of Medicine – Universidad Científica del Sur} & \textsc{Lima – Peru} \\
\multicolumn{2}{p{18cm}}{%
\textsc{Introduction to Epidemiology:} I teach three sections of \textasciitilde 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts.
} \\
\\
\textbf{Teaching Assistant} & \textbf{Mar 2024 – Jun 2024} \\
\textsc{College of Arts \& Sciences – University of Washington} & \textsc{Seattle – USA} \\
\multicolumn{2}{p{18cm}}{%
\textsc{Introduction to Molecular and Cellular Biology:} Led two laboratory practice sessions with \textasciitilde 25 undergraduate students each, covering fundamental molecular and cellular biology experiments.
} \\
\end{longtable}
\vspace{-0.75em}
\subsection{Mentoring}
\vspace{-0.75em}
\subsubsection{Undergraduate thesis}
\vspace{-0.75em}
```{r mentees_table}
#| results: asis
mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
mentees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
       ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(year))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```