---
format:
  pdf:
    output-file: DelCastillo_Resume.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r setup}
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")
```

\begin{center}
\huge{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}
\section*{Professional Summary}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

Epidemiologist and physician with an MPH in Epidemiology and extensive experience translating real-world evidence from claims, electronic health records, linked administrative data, cohorts, and observational studies across the UK, US, and Peru into meaningful insights. Strong background in causal inference, survival analysis, evidence synthesis, and communicating findings to both specialist and lay audiences. Adept at integrating state-of-the-art tools, such as large language models, into analytical workflows to support coding and research. Particularly interested in applying this skill set to advance non-communicable disease drug development in global, industry environments.

\section*{Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH) – Epidemiology} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington} & \textsc{Seattle - USA} \\

&\\

\textbf{Doctor of Medicine (MD)} & \textbf{Mar 2014 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos} & \textsc{Lima - Peru} \\
\end{longtable}
\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\textbf{Programming:} R, Stata, SQL (MySQL), Python\
\textbf{Cloud Computing:} Slurm HPC, Docker, Linux environments (bash)\
\textbf{Tools:} VS Code, Jupyter, Quarto, \LaTeX, Shiny (R), ArcGIS, Power BI, Git version control (GitHub, Bitbucket, GitLab), REDCap, Office 365 Suite (Word, Excel, PowerPoint), Generative AI tools for coding (Claude Code)\
\textbf{Data Standards:} HIPAA, ICH E6, HL7 FHIR, GDPR, UK GDPR, DPA 2018, ICD-10/ICD-9/SNOMED\
\textbf{Packages:} \texttt{tidyverse}, \texttt{data.table}, \texttt{ggplot2}, \texttt{lme4}, \texttt{survival}, \texttt{sf}, \texttt{cmprsk}, \texttt{mice}, \texttt{geepack}, \texttt{metafor}, \texttt{rstan}, \texttt{caret}, \texttt{ivreg}, \texttt{Pandas}, \texttt{NumPy}, \texttt{Matplotlib}, MR-BRT\
\textbf{Statistical methods:} Bayesian hierarchical modelling (MCMC), GLM/GLMM, sample-size & power, time-to-event models, propensity score matching, marginal structural models, competing risks, multiple imputation, meta-analysis, crosswalking, uncertainty quantification (confidence & posterior intervals)\
\textbf{Languages:} English (fluent), Spanish (native)\
\textbf{Core Competencies:} Real-world evidence generation, literature reviews, project coordination, stakeholder communication, scientific writing, problem solving, mentorship

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Research Assistant – Epidemiology} & \textbf{Dec 2025 – Current} \\
\textsc{School of Health and Wellbeing – University of Glasgow} & \textsc{Glasgow - UK} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
 \item Generated real-world evidence on the health effects of unemployment using nationally representative longitudinal survey data and a parametric g-formula.
 \item Estimated the causal effects of relative income on all-cause mortality using linked administrative data and inverse-probability-weighted marginal structural models.
 \item Supported evidence synthesis and meta-analysis of employability schemes on health outcomes for a systematic review and meta-analysis of the health effects of active labor market policies.
\end{itemize}
} \\
\\
\textbf{Research Assistant – Clinical Informatics} & \textbf{Jul 2024 – Jun 2025} \\
\textsc{Institute for Health Metrics and Evaluation} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Developed data-driven inputs for Bayesian hierarchical meta-regression models through a systematic review and a meta-analysis to estimate the burden and clinical outcomes of lower respiratory tract infections worldwide.
  \item Analysed large-scale real-world data, including structured and unstructured electronic health records from 2 countries with 60+ million records, to generate epidemiological summaries of GBD risk factors stratified by age and sex.
  \item Executed MCMC-based analyses with data-driven priors and uncertainty propagation to estimate overlap among inclusion health populations in 22 high-income countries and compute population-attributable fractions and standardized mortality ratios.
\end{itemize}
} \\
\newpage
\textbf{Real-World Evidence Consultant – Health Technology Assessment} & \textbf{Jan 2023 – Jan 2024} \\
\textsc{Social Security System (ESSALUD)} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Generated real-world evidence from harmonised claims and inpatient data from 20+ hospitals (>5 million encounters) using ICD-10 phenotyping and probabilistic linkage.
  \item Built regression and survival analysis pipelines in R with quality control for reimbursement policy analyses and healthcare decision-making.
  \item Developed state-transition models to evaluate reimbursement policy options with deterministic and probabilistic sensitivity analyses.
\end{itemize}
} \\
\\
\textbf{Epidemiology Trainee} & \textbf{Mar 2019 – Aug 2023}\\
\textsc{CRONICAS Center of Excellence in Chronic Diseases} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
  \item Analysed longitudinal data from population cohorts and randomised trials using generalised linear methods and survival analysis in cardiometabolic epidemiology.
  \item Conducted exploratory analyses of clinical, demographic, and biological biomarkers to support research grant proposals and scientific outputs.
  \item Co-authored 5 scientific manuscripts involving longitudinal analyses and machine learning models.
\end{itemize}
} \\
\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia} & \textsc{Lima - Peru} \\
& \\
\textbf{Non-Certificate Trainee in Demographic Methods} & \textbf{Sep 2024 – Jun 2025} \\
\textsc{Center for Studies in Demography and Ecology – University of Washington} & \textsc{Seattle – USA} \\
\end{longtable}

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\textbf{2023} & CITI Program, Good Clinical Practice (ICH E6), Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2021} & Peruvian Medical Board, License No. 94534 \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}

```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
       ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(year))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```