---
format:
  pdf:
    output-file: delcastillo_resume.pdf
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 9pt
    geometry:
      - margin=0.5in
      - heightrounded
      - includefoot
      - footskip=0.5in
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r setup}
#| include: false
#| message: false
#| eval: true

knitr::opts_chunk$set(
fig.path = "figs/",
fig.width = 7.252,
fig.height = 4,
comment = "#>",
fig.retina = 3
)

source("functions.R")

# Store IDs
gscholar_id <- "iNdNU5QAAAAJ"
gscholar_page <- paste0("https://scholar.google.com/citations?user=", gscholar_id)

# Google Scholar text
text_gs <- invisible(gscholar_stats(url = gscholar_page))
```

\begin{center}
\huge{\uline{\textbf{Darwin Del Castillo, MD, MPH}}} \\
\vspace{2.5pt}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{LinkedIn:} \href{https://www.linkedin.com/in/darwin-del-castillo/}{darwin-del-castillo}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{Email:} \href{mailto:ddelcastillo.f@gmail.com}{ddelcastillo.f@gmail.com}
\end{minipage}
\begin{minipage}[c]{0.28\textwidth}
\centering \textbf{GitHub:} \href{https://github.com/ddelcastillof}{github.com/ddelcastillof}
\end{minipage}
\vspace{-2.5pt}
\end{center}

\section*{Scientific Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Master of Public Health (MPH)} & \textbf{Sep 2023 – Jun 2025} \\
\textsc{University of Washington, Seattle - USA} & \\

&\\

\textbf{Doctor of Medicine (MD)} & \textbf{Mar 2013 – Dec 2020} \\
\textsc{Universidad Nacional Mayor de San Marcos, Lima - Peru} &\\
\end{longtable}

\section*{Skills}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\textbf{Programming:} SQL (MySQL), R, Stata, Python \
\textbf{Cloud Computing:} Slurm HPC, Docker, Linux environments (bash) \
\textbf{Tools:} VS Code, Quarto, \LaTeX, Shiny (R), ArcGIS, Power BI, REDCap, Office 365 Suite, Git version control (GitHub, Bitbucket, GitLab) \
\textbf{Data Standards:} HIPAA, ICH E6, HL7 FHIR, GDPR, UK GDPR, DPA 2018, ICD-10/ICD-9/SNOMED \
\textbf{Packages:} \texttt{tidyverse}, \texttt{ggplot2}, \texttt{lme4}, \texttt{survival}, \texttt{sf}, \texttt{spdep}, \texttt{cmprsk}, \texttt{mice}, \texttt{geepack}, \texttt{metafor}, \texttt{rstan}, \texttt{caret}, \texttt{Pandas}, \texttt{NumPy}, \texttt{Matplotlib}, MR-BRT \
\textbf{Languages:} English (fluent), Spanish (native) \
\textbf{Core Competencies:} Data analysis, teamwork, problem solving, science communication, mentorship

\section*{Professional Experience}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}

\textbf{Graduate Research Assistant} & \textbf{Jul 2024 – Jun 2025} \\
\textsc{Institute for Health Metrics and Evaluation} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Developed hyperparameters for a Bayesian hierarchical meta‑regression model to estimate prevalence, incidence, and clinical‐outcome occurrence of lower‑respiratory‑tract infections across 80 countries.
\item Executed an MCMC using data-driven priors and uncertainty propagation to estimate the probabilistic overlap between inclusion health groups in 22 high-income countries.
\item Produced a global map of study locations using GBD 2023 georeference data to visualize geographic coverage and data gaps, informing meta-analysis data sources.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant} & \textbf{Jun 2024 – Mar 2025} \\
\textsc{Department of Global Health – University of Washington} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Coordinated a pragmatic mixed-methods study to explore barriers and facilitators in \textgreater10 low-resource Peruvian hospitals.
\item Designed and deployed the electronic CRF and wrote the data-management plan to manage input data from the mixed-methods study, solving 350+ data entry queries during project deployment. 
\item Co-developed communication strategies with stakeholders to disseminate complex findings among healthcare policymakers.
\end{itemize}
} \\
\\
\textbf{Graduate Research Assistant}  & \textbf{Sep 2023 – Mar 2024} \\
\textsc{Health Population Research Center – University of Washington} & \textsc{Seattle - USA} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize} 
\item Maintained and stored sociodemographic and utilisation data as part of a clinical trial post-assessment survey using electronic data capture platforms.
\item Translated IRB submission materials from Spanish to English for the Alzheimer’s Disease Research Center.
\item Analysed engagement and outreach data into visualisation tools and summary tables, enabling programme managers to make adjustments to recruitment strategies.
\end{itemize}
} \\
\\
\textbf{RWE Consultant} & \textbf{Jan 2023 – Jan 2024} \\
\textsc{Health Technology Assessment and Research Institute} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Integrated surveillance and clinical data into statistical burden models to support national health technology assessment and prioritisation processes.
\item Conducted budget impact and cost-effectiveness analysis to prioritise funding for high-impact health interventions under national budgets.
\item Synthesised results from these models into evidence summaries to policymakers and health practitioners, supporting strategic purchasing decisions for the Peruvian Social Security System.
\end{itemize}
} \\
\newpage
\textbf{Data Manager} & \textbf{Mar 2022 - Mar 2023}\\
\multicolumn{2}{p{18cm}}{\textbf{Via Libre Association}} \\
\multicolumn{2}{p{18cm}}{\textbf{Lima (Peru)}} \\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Managed patient databases and tracked data collection across multiple clinical sites using REDCap and iMedidata systems.
\item Resolved data queries and quality issues while monitoring protocol compliance and adverse event reporting.
\item Created data cleaning reports and recruitment dashboards to support study monitoring and database finalization.
\end{itemize}
} \\
\\
\textbf{Research Assistant} & \textbf{Mar 2019 – Aug 2023}\\
\textsc{CRONICAS Center of Excellence in Chronic Diseases} & \textsc{Lima – Peru}\\
\multicolumn{2}{p{18cm}}{%
\begin{itemize}
\item Resolved and stored harmonised datasets across 8+ years of longitudinal and clinical trial data using R and REDCap, enabling consistent analytics and timely access for interdisciplinary research teams.
\item Analysed real-world evidence and conducted preliminary analyses that strengthened proposals targeting hypertension, diabetes, cancer, and multimorbidity, securing \$300\,k in competitive funding.
\item Co-authored 5 peer-reviewed manuscripts as part of international collaborations, communicating epidemiological findings for academic and lay audiences.
\end{itemize}
} \\
\end{longtable}

\section*{Additional Education}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}

\begin{longtable}{p{14cm}>{\raggedleft\arraybackslash}p{4cm}}
\textbf{Professional Certificate in Clinical Research} & \textbf{Sep 2021 – Apr 2022} \\
\textsc{Universidad Peruana Cayetano Heredia} & \textsc{Lima - Peru}\\
& \\
\textbf{Non-Certificate Trainee in Demographic Methods} & \textbf{Sep 2024 – Current} \\
\textsc{Center for Studies in Demography and Ecology – University of Washington} & \textsc{Seattle – USA} \\
\end{longtable}
\end{longtable}

\section*{Teaching Professional Activities}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Teaching}
\vspace{-1em}
\begin{longtable}{>{\raggedright\arraybackslash}p{14cm} p{4cm}}
\textbf{Lecturer} & \textbf{Mar 2025 – Current} \\
\textsc{School of Medicine – Universidad Científica del Sur} & \textsc{Lima – Peru} \\
\multicolumn{2}{p{18cm}}{%
\textsc{Introduction to Epidemiology:} I teach three sections of \textasciitilde 15 fourth-year medical students each, focusing on basic clinical epidemiology concepts, including study designs, bias identification, \& basic epidemiological surveillance concepts.
} \\
\\
\textbf{Teaching Assistant} & \textbf{Mar 2024 – Jun 2024} \\
\textsc{College of Arts \& Sciences – University of Washington} & \textsc{Seattle – USA} \\
\multicolumn{2}{p{18cm}}{%
\textsc{Introduction to Molecular and Cellular Biology:} Led two laboratory practice sessions with \textasciitilde 25 undergraduate students each, covering fundamental molecular and cellular biology experiments.
} \\
\end{longtable}
\vspace{-0.75em}
\subsection{Mentoring}
\vspace{-0.75em}
\subsubsection{Undergraduate thesis}
\vspace{-0.75em}
```{r mentees_table}
#| results: asis
mentees <- get_cv_sheet('advising') |>
  arrange(date_start) |> 
  mutate(
    date = paste0(' (',  date_start, ' to ', date_stop, ').'),
    citation = ifelse(
      is.na(title), name, paste0(name, ', ', enquote(title))
    ),
    citation = paste0(citation, ', ', institution, ' ', date), 
    citation = ifelse(
        is.na(defense_date), citation, 
        paste0(citation, ' _Defense date: ', defense_date, '_.')
    )
  )
mentees |> 
  filter(complete == 0) |>
  make_bullet_list_filtered("ug")
```

\section*{Licensure and certification}
\vspace{-1.5em}
\textcolor{darkgray}{\rule{\textwidth}{0.5pt}}
\begin{longtable}{>{\raggedright\arraybackslash}p{1.5cm} p{16.5cm}}
\textbf{2024} & National Registry of Investigators, RENACYT-CONCYTEC, Investigator Level VII (P0160977) \\
\textbf{2023} & CITI Program, Good Clinical Practice and ICH, Credential ID 65079238 \\
\textbf{2023} & CITI Program, Human Subjects Learners, Credential ID 65079240 \\
\textbf{2023} & CITI Program, Biomedical Responsible Conduct of Research, Credential ID 65079239 \\
\textbf{2021} & Peruvian College of Physicians, Membership No. 94534 \\
\end{longtable}

\section*{Publications \hspace{0.75cm} ORCID: 0000-0002-8609-0312}
\vspace{-1.5em}
\textcolor{gray}{\rule{\textwidth}{0.5pt}}
\subsection{Peer-reviewed publications}
```{r importing pubs, include = F, echo = F}
pubs <- get_cv_sheet('pubs') |>
  mutate(
    journal  = ifelse(is.na(journal_abbv), '', paste0('\\textbf{','\\uline{', journal_abbv, '}','}')),
    number   = ifelse(is.na(number), '', paste0(number, '.')),
    doi      = case_when(is.na(doi) ~ '',
                         doi == 'Submitted under consideration' ~ doi,
                         TRUE ~ paste0('Available at: [', doi, '](', 'https://doi.org/', doi, ')')
       ),
    year     = paste0("(", year, ")"),
    title    = enquote(title),
    conference = ifelse(is.na(conference_name), '', paste0('\\textbf{','\\uline{', conference_name, '}','}')),
    organization = ifelse(is.na(organization_name), '', paste0(organization_name, '.')),
    # Different citation formats for different categories
    citation = case_when(
      category == "conference" ~ paste(author, year, title, conference, 
                                      paste0(organization, ", ", place)),
      category == "white_paper" ~ paste(author, year, title, organization_name, 
                                      paste0(place)),
      category == "peer_reviewed" ~ paste(author, year, title, journal, number, doi),
      category == "thesis" ~ paste(author, year, title, journal, organization)
    )
  ) |> 
  arrange(desc(year))
```

```{r peer reviewed pubs}
#| results: asis
#| name: peer reviewed pubs
make_bullet_list_filtered(pubs, "peer_reviewed")
```

\subsection{Conference abstracts}
```{r conference abstracts}
#| results: asis
#| name: conference abstracts
make_bullet_list_filtered(pubs, "conference")
```